Local Spectral Clustering of Density Upper Level Sets

### 2019-01-23 icml/icml_local_density_clustering.tex
Cleaned up RJT comments
A bit of edits and corrections.  Still haven't gone through Sect 3 (or 4)

\paragraph{External Connectivity: Normalized Cut.}

@@

\paragraph{Internal Connectivity: Inverse Mixing Time.}

For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Abf_S,\Dbf_S$
be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
random walk matrix as usual, $\Wbf = \Dbf_S^{-1} \Abf_S$, and for $v \in V$,
write 
\begin{equation}
\label{eqn: random_walk}
q_{vu}^{(t)} = e_v\Wbf_S^t e_u
\end{equation}
for the $t$-step transition probability of a random walk over $G[S]$
originating at $v$.\footnote{Given a starting node $v$ and and a random walk
  defined by transition probability matrix $\mathbf{P}$, the rotation $e_v
  \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
  steps.}   Also write \smash{$\tilde\pibf = (\tilde\pi_{u})_{u \in S}$} for the 
  stationary distribution of this random walk.  (Given the definition of
  $\Wbf_S$, it is well-known that the stationariy distribution is given by
  \smash{$\tilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)

Our internal connectivity parameter will capture the time it takes for the
random walk over $G[S]$ to mix (approach the stationary distribution)
uniformly over $S$.  For this, we first define \emph{relative pointwise mixing
  time} of $G[S]$ as 
\begin{equation*}
\tau_{\infty}(\qbf; G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} -
      \tilde\pi_u|}{\tilde\pi_u} \leq \frac{1}{4}, \; \text{for $u,v \in V$}}, 
\end{equation*}
where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. Now our internal 
connectivity parameter is simply the inverse mixing time,
\begin{equation}
\label{eqn: inv_mixing_time}
\Psi(S; G) = \frac{1}{\tau_{\infty}(\qbf; G[S])}.
\end{equation}

@@

\begin{enumerate}
\item In Section \ref{sec: PhiPsi}, we derive in Theorem \ref{thm:
    conductance_upper_bound} an upper bound on the normalized cut of a
  (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
  conditions (precluding clusters that are too thin and long).

@@

\section{Cluster Quality Critera Bounds for Density Clusters}  
\label{sec: PhiPsi}

\subsection{Assumptions}

In order to provide meaningful bounds on the normalized cut and inverse mixing
time of an empirical density cluster, we must introduce conditions on the
density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the ball of
radius $r$ centered at $x$.  Given a set $\Aset \subseteq \Rd$ and $\sigma > 0$,
define $\Asig = \Aset + B(0,\sigma) = \{y \in \Rd: \inf_{x \in \Aset} \norm{y - 
    x} \leq \sigma\}$, which we call the $\sigma$-expansion of $\Aset$.

We are now ready to give the conditions, stated with respect to a density
cluster $\Cset \in \Cbb_f(\lambda)$, for some $\lambda > 0$, and an expansion 
parameter $\sigma > 0$.

@@

In the next several subsections, we will derive bounds on the cluster quality
criteria evaluated on (thickened) density clusters. For notational simplicity,
hereafter for $S \subseteq V$, we will denote $\Phi(S; G_{n,r})$ by
$\Phi_{n,r}(S)$, and likewise with $\Psi(S; G_{n,r})$ and $\Psi_{n,r}(S)$. We
will also use $\nu$ for Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for 
the measure of the unit ball $B=B(0,1)$. 
% RJT: you had B(0,d) before ... just check this should have been B(0,1)

@@

We begin by upper bounding the normalized cut of $\Cset_\sigma[\Xbf]$.  (In the
theorem, the upper bound on the density in Assumption \ref{asmp: 
  bounded_density} will not actually be needed, so we omit the parameter
$\Lambda_\sigma>0$ from the theorem statement.)

@@

\begin{remark}
The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
$$
f(x) = \lambda - \dist(x,\Asig)^{\gamma},
$$
% RJT: is this correct (is this what you meant)?  Original formula is below
% $$
% f(x)  = \begin{cases}
%   \lambda &\text{for $x \in \Asig$}, \\
%   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
% \end{cases}
% $$
we have that for $n$ on the order of the lower bound in \eqref{eqn: 
  conductance_sample_complexity}, 
\begin{equation*}
  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
    \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
\end{equation*}
with probability at least $1 - \delta$, for some constant $c$. (Note that the
factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
\end{remark}

@@

We lower bound the inverse mixing time of $\Csig[\Xbf]$.

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound_nonconvex}
Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
$$
\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
    \lambda_{\sigma}}} \leq \epsilon, 
$$
where \smash{$\mu = \log(\frac{2D}{r})$}, we have
\begin{multline}
\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq (d \log \mu + c_{\lambda}) \cdot \\  
\left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
    \log \mu + c_{\lambda}\right)\right),
\end{multline}
with probability at least $1 - \delta$, where $c_1,c_2,c_3>0$ are constants
depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/
\lambda_{\sigma}^2)$.   
\end{theorem}
% RJT: saying that c_1,c_2,c_3 depend on the dimension is a little odd/weak.
% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
% will swamp the linear factor of ....

@@

\subsection{Tigher Lower Bound Under Convexity}

It is possible to sharpen the dependency on $d$ in 
\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
additional assumption.
\begin{enumerate}[label=(A\arabic*)]
\setcounter{enumi}{4}
\item 
\label{asmp: convex}
\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
\end{enumerate}
% RJT: do we need C to satisfy this, or Csig?  Not sure I know why the former
% matters ...

@@

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound}
Assume the conditions of Theorem \ref{thm:
  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
  convex}. Then for any $r < \sigma/4d$, the following holds with probability 1:  
\begin{align}
\label{eqn: inverse_mixing_time_lower_bound}
  \limsup_{n \to \infty} \, &\Psi_{n,r}(\Csig[\Xbf])^{-1} \leq \nonumber \\ 
&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
\end{align}
where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
\end{theorem}
% RJT: this was a lower bound on 1/\Psi and I changed it to \Psi ... just
% checking

@@

\begin{remark}
We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
to those in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part
by working with a generalization of the conductance, the \emph{conductance
  function},
\begin{equation*}
\widetilde{\Phi}_n(t) = 
\min_{\substack{S \subseteq \Csig[\Xbf] \\ \tilde\pi(S) \leq t}} \Phi(S; G_{n,r}[\Csig[X]]) 
\end{equation*}
where \smash{$\tilde\pi$} is the stationary distribution over
$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
known upper bound of mixing time by  
\begin{equation}
\label{eqn: average_conductance}
\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
\end{equation}
which results in a tighter bound than merely using the conductance when
\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.

Our proof relies on a novel (to the best of our knowledge) uniform lower bound
on this conductance function over $G_{n,r}$ in terms of a population-level
analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
a mixing time bound (with respect to total variation distance) of order $d
D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
pointwise distance (which is known to be a stricter metric). 
\end{remark}

\begin{remark}
  The convexity requirement is necessary only to lower bound the
  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any bound on
  \smash{$\widetilde{\Phi}_{\Pbb,r}$} which does not require convexity could
  immediately be plugged into the machinery of the proof of Theorem \ref{thm:
    inverse_mixing_time_lower_bound} to achieve a corresponding result. Recent
  work \citep{abbasi17} has developed such population-level bounds on the
  conductance function, however the Markov chain dealt with there is somewhat
  different than the one we consider.   
\end{remark}

@@

For PPR to successfully recover density clusters, the ratio $\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.

We introduce
\begin{align*}
\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) & := \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} \\
1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) & := \left(d \log \mu + c_{\lambda} \right) \cdot \nonumber \\ 
& \left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + c_{\lambda}\right)\right)
\end{align*}

@@

\begin{remark}
	We note that larger constants than $40 \cdot 36$ allow for wider range of the parameters in $\eqref{eqn: initialization}$. 
\end{remark}
\paragraph{Approximate cluster recovery via PPR.}

@@

For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.
\begin{lemma}[PPR clustering]
	\label{lem: ppr_cluster}
	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$. Letting 
	\begin{equation*}
	\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G)
	\end{equation*}
	the following guarantees hold:
	\begin{align*}
	\vol(\widehat{C} \setminus A) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
	\end{align*}
\end{lemma}

>>>>

\paragraph{External Connectivity: Normalized Cut}

@@

\paragraph{Internal Connectivity: Inverse Mixing Time}

For $S \subseteq V$, denote by $G[S] = (S, E_S, w_S)$ the subgraph induced by 
$S$ (where the edges are $E_S = E \cap (S \times S)$). Let $\Abf_S,\Dbf_S$
be the adjacency matrix and degree matrix, respectively, of $G[S]$.  Define the
random walk matrix as usual, $\Wbf = \Dbf_S^{-1} \Abf_S$, and for $v \in V$,
write 
$$
q_{vu}^{(t)} = e_v\Wbf_S^t e_u
$$
for the $t$-step transition probability of a random walk over $G[S]$
originating at $v$.\footnote{Given a starting node $v$ and and a random walk
  defined by transition probability matrix $\mathbf{P}$, the rotation $e_v
  \mathbf{P}^t$ is used to denote the distribution of the random walk after $t$
  steps.}   Also write \smash{$\widetilde\pibf = (\widetilde\pi_{u})_{u \in S}$}
for the stationary distribution of this random walk.  (Given the definition of 
$\Wbf_S$, it is well-known that the stationariy distribution is given by
\smash{$\widetilde\pi_{u} = (\Dbf_{S})_{uu} / \vol(S; G[S])$}.)

Our internal connectivity parameter will capture the time it takes for the
random walk over $G[S]$ to mix (approach the stationary distribution)
uniformly over $S$.  For this, we first define \emph{relative pointwise mixing
  time} of $G[S]$ as 
$$
\tau_{\infty}(G[S]) = \min\set{ t: \frac{|q_{vu}^{(m)} - 
      \widetilde\pi_u|}{\widetilde\pi_u} \leq \frac{1}{4}, 
    \; \text{for $u,v \in V$}},  
$$
%where \smash{$\qbf = (\qbf_v^{(1)}, \qbf_v^{(2)}, ...)_{v \in V}$}, and
%\smash{$\qbf_v^{(m)} = (q_{vu}^{(m)})_{u \in V}$}. 
% RJT: I got rid of the notational dependence on \qbf, because these quantities
% are in turn just defined in terms of the induced subgraph G[S]
Now our internal connectivity parameter is simply the inverse mixing time, 
\begin{equation}
\label{eqn: inv_mixing_time}
\Psi(S; G) = \frac{1}{\tau_{\infty}(G[S])}.
\end{equation}

@@

\begin{enumerate}
\item In Section \ref{sec: cluster_quality_bounds}, we derive in Theorem
  \ref{thm: conductance_upper_bound} an upper bound on the normalized cut of a  
  (thickened) empirical density cluster $\Csig[\Xbf]$, under natural geometric 
  conditions (precluding clusters that are too thin and long).

@@

\section{Cluster Quality Critera Bounds for Density Clusters}  
\label{sec: cluster_quality_bounds}

\subsection{Geometric Conditions on Density Clusters}

In order to provide meaningful bounds on the normalized cut and inverse mixing
time of an empirical density cluster, we must introduce conditions on the
density $f$. Let $B(x,r) = \{y \in \Rd: \norm{y - x} \leq r\}$ be the closed
ball of radius $r \geq 0$, centered at $x \in \Rd$.  Given a set $\Aset
\subseteq \Rd$ and $\sigma > 0$, define $\Asig = \Aset + B(0,\sigma) = \{y \in
\Rd: \inf_{x \in \Aset} \norm{y - x} \leq \sigma\}$, which we call the
$\sigma$-expansion of $\Aset$.

We are now ready to give the conditions, stated with respect to a density
cluster $\Cset \in \Cbb_f(\lambda)$, for some threshold $\lambda > 0$, and an
expansion parameter $\sigma > 0$.

@@

In the next several subsections, we will derive bounds on the cluster quality
criteria evaluated on (thickened) density clusters. For notational simplicity,
hereafter for $S \subseteq V$, we will abbreviate $\Phi(S; G_{n,r})$ by
$\Phi_{n,r}(S)$, and similarly, $\Psi(S; G_{n,r})$ by $\Psi_{n,r}(S)$, and
$\tau_{\infty}(G_{n,r}[S])$ by $\tau_{n,r}(S)$. We will also use $\nu$ for
Lebesgue measure on $\Rd$, and $\nu_d = \nu(B)$ for the measure of the unit ball
$B=B(0,1)$.  
% RJT: you had B(0,d) before ... just check this should have been B(0,1)

@@

We start with an upper bound on the normalized cut \eqref{eqn: norm_cut} of 
$\Cset_\sigma[\Xbf]$. (In the theorem, the upper bound on the density in
Assumption \ref{asmp: bounded_density} will not actually be needed, so we omit
the parameter $\Lambda_\sigma>0$ from the theorem statement.)

@@

\begin{remark}
The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
$$
f(x) = \lambda - \dist(x,\Asig)^{\gamma},
$$
% RJT: is this correct (is this what you meant)?  Original formula is below
% $$
% f(x)  = \begin{cases}
%   \lambda &\text{for $x \in \Asig$}, \\
%   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
% \end{cases}
% $$
we have that for $n$ on the order of the lower bound in \eqref{eqn: 
  conductance_sample_complexity}, 
$$
  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
    \frac{r^{\epsilon+1}}{\epsilon+1})}{\lambda} - \epsilon,
$$
with probability at least $1 - \delta$, for some constant $c$. (Note that the
factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
\end{remark}

@@

Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of 
$\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) =
1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time. 
% RJT: note I changed the next two theorems to be upper bounds on the mixing
% time.  Upper bounds on the inverse inverse mixing time, which was a bit
% superfluous.  Just make sure that the supplement is in sync with this

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound_nonconvex}
Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
$$
\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
    \lambda_{\sigma}}} \leq \epsilon, 
$$
where \smash{$\mu = \log(\frac{2D}{r})$}, we have
\begin{multline}
\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
\tau_{n,r}(\Csig[\Xbf]) \leq (d \log \mu + c_{\lambda}) \cdot \\  
\left(c_1 + c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
    \log \mu + c_{\lambda}\right)\right),
\end{multline}
with probability at least $1 - \delta$, where $c_1,c_2>0$ are constants
depending only on the dimension $d$, and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
\lambda_{\sigma}^2)$.   
\end{theorem}
% RJT: saying that c_1,c_2 depend on the dimension is a little odd/weak.
% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
% will swamp the linear factor of ....

@@

\subsection{Tighter Lower Bound Under Convexity}

It is possible to sharpen the dependency on $d$ in 
\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
additional assumption.
\begin{enumerate}[label=(A\arabic*)]
\setcounter{enumi}{4}
\item 
\label{asmp: convex}
\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
\end{enumerate}

@@

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound}
Assume the conditions of Theorem \ref{thm:
  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
  convex}. Then for any $0 < r < \sigma/4d$, the following holds with
probability 1:   
\begin{align}
\label{eqn: inverse_mixing_time_lower_bound}
  \limsup_{n \to \infty} \, &\tau_{n,r}(\Csig[\Xbf]) \leq \nonumber \\ 
&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
\end{align}
where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
\end{theorem}

@@

\begin{remark}
We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
to those in Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part 
by working with a generalization of the conductance, the \emph{conductance
  function},
$$
\widetilde{\Phi}_n(t) = 
\min_{\substack{S \subseteq \Csig[\Xbf] \\ \widetilde\pi(S) \leq t}} 
\Phi(S; G_{n,r}[\Csig[X]]),
$$
where \smash{$\widetilde\pi$} is the stationary distribution over
$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
known upper bound of mixing time by  
\begin{equation}
\label{eqn: average_conductance}
\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
\end{equation}
which results in a tighter bound than merely using the conductance when
\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.

Our proof relies on a novel (to the best of our knowledge) uniform lower bound
on this conductance function over $G_{n,r}$ in terms of a population-level
analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Plugging
\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
a mixing time bound (with respect to total variation distance) on the order $d 
D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
pointwise distance (which is known to be a stricter metric). 
\end{remark}

\begin{remark}
  The convexity condition is only needed to lower bound 
  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any lower bound on
  \smash{$\widetilde{\Phi}_{\Pbb,r}$} could be directly plugged into the 
  machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
  to yield an alternative result. In recent work, \citet{abbasi17} developed new
  population-level bounds on the conductance function (without requiring
  convexity), however the Markov chain dealt with there is somewhat different 
  than the one we consider.    
\end{remark}

@@

\subsection{Well-Conditioned Density Clusters}

For PPR to successfully recover density clusters, the ratio
$\Phi_{n,r}(\Csig[\Xbf])/\Psi_{n,r}(\Csig[\Xbf])$ must be small.  Let us
introduce the following notation for the upper bounds in Theorems 
\ref{thm: conductance_upper_bound} and \ref{thm:
  inverse_mixing_time_lower_bound_nonconvex}:
\begin{align*}
\mathbf{\Phi}(\sigma, \lambda,\lambda_{\sigma},\gamma) 
&= \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
  \frac{\sigma^{\gamma}}{\gamma+1})}{\lambda_{\sigma}}, \\
1 / \mathbf{\Psi}(\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D) 
&= \left(d \log \mu + c_{\lambda} \right) \cdot \\ 
& \left(c_1 + c_2
  \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d \log \mu + 
  c_{\lambda}\right)\right)
\end{align*}
(where all constants $\lambda_\sigma,c_1,c_2, c_\lambda>0$ are as in these 
theorems).

@@

\begin{remark}
	We note that larger constants than $40 \cdot 36$ allow for wider range of the parameters in $\eqref{eqn: initialization}$. 
\end{remark}
\paragraph{Approximate cluster recovery via PPR}

@@

For $G = (V,E)$ consider some $A \subseteq V$, and let $\Phi(A; G)$ and $\Psi(A; G)$ be defined as in (\ref{eqn: norm_cut}) and (\ref{eqn: inv_mixing_time}), respectively.r
\begin{lemma}[PPR clustering]
	\label{lem: ppr_cluster}
	There exists a set $A^g \subseteq A$ with $\vol(A^g;G) \geq \vol(A;G)/2$ such that the following statement holds: Choose any $v \in A^g$, fix $\alpha = 9 / 10 \Psi(A; G)$, and compute the page rank vector $\pbf(v,\alpha; G)$. Letting 
	\begin{equation*}
	\widehat{C} = \argmin_{\beta \in [\frac{1}{8}, \frac{1}{2}]} \Phi(S_{\beta}; G)
	\end{equation*}
	the following guarantees hold:
	\begin{align*}
	\vol(\widehat{C} \setminus A) & \leq \frac{24 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
	\vol(A \setminus \widehat{C})  & \leq \frac{30 \Phi(A; G)}{\Psi(A; G)} \vol(A) \\
	\Phi(\widehat{C}; G) & = O\left(\frac{\Phi(A; G)}{\sqrt{\Psi(A; G)}}\right)
	\end{align*}
\end{lemma}
